Landscape composition and beneficial insects

### 2020-07-02 manuscript/manuscript_outline.Rmd
Added some refs

* The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways
  + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
  + Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees 
  + @drapela2011 also found that _Pardosa agrestis_ had higher activity density in areas with woody trees and shrubs
  + While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2011; @kowal2011], _P. distincta_ appears to be less sensitive to disturbances than _P. moesta_ [@collins1996; @wade2010]
  + We found that roads clearly acted as an early source and a late sink of _P. moesta_
  + Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source for _P. moesta_
  + @oberg2007

  a wandering-active predation strategy [@young1990],

>>>>

* The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways
  + Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008]
  + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
  + Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees for overwintering [but _P. distincta_ are known to be active during the winter; @aitchison1984]
  + @drapela2011 also found that _Pardosa agrestis_ had higher activity density in areas with woody trees and shrubs
  + @moring1994 showed that _P. distincta_ were more active in grassy substrates
  + While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], _P. distincta_ appears to be less sensitive to disturbances than _P. moesta_ [@collins1996; @wade2010]
  + We found that roads clearly acted as an early source and a late sink of _P. moesta_
  + Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source for _P. moesta_
